---
title: "This is a title"
author: "And this is my name"
subtitle: "A sub-title should you want to add one"
institute: "Indian School of Business"
format: 
  revealjs:
      logo: logo.png
---

## This is where you put the slide title

- Insert bullet one
- Insert bullet two
- And many more

## This is how you mark the beginning of another slide

::: {.incremental}
- The content here ...
- Comes incrementally,
- With every next click.
:::


## There is another way of doing this

Here is the content before the pause

. . .

This is the content after the pause

## You can standardize the previous format

And have it without the pauses.

::: {.nonincremental}
- Just Existing
- Like That
:::



## Slide with Code


::: {.panel-tabset}

### Tab A

Content for `Tab A`

-Follows markdown syntax like usual

### Tab B

Content for `Tab B`

-regardless of what tab it is on.

:::

## You can animate code blocks for some flair  {auto-animate="true"}

```r
# Fill in the spot we created for a plot
output$phonePlot <- renderPlot({
  # Render a barplot
})
```

## You can animate code blocks for some flair {auto-animate=true}

```r
# Fill in the spot we created for a plot
output$phonePlot <- renderPlot({
  # Render a barplot
  barplot(WorldPhones[,input$region]*1000, 
          main=input$region,
          ylab="Number of Telephones",
          xlab="Year")
})
```

## Line Highlighting

-   Highlight specific lines for emphasis
-   Incrementally highlight additional lines

``` {.python code-line-numbers="4-5|7|10"}
import numpy as np
import matplotlib.pyplot as plt
r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(subplot_kw={'projection': 'polar'})
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

## Executable Code

```{r}
#| echo: true
#| fig-width: 10
#| fig-height: 4.5
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess")
```



## Fragments

Incremental text display and animation with fragments:

<br/>

::: {.fragment .fade-in}
Fade in
:::

::: {.fragment .fade-up}
Slide up while fading in
:::

::: {.fragment .fade-left}
Slide left while fading in
:::

::: {.fragment .fade-in-then-semi-out}
Fade in then semi out
:::

. . .

::: {.fragment .strike}
Strike
:::

::: {.fragment .highlight-red}
Highlight red
:::

## Extras this slide onward

## Auto-Animate {auto-animate="true" auto-animate-easing="ease-in-out"}

Automatically animate matching elements across slides with Auto-Animate.

::: r-hstack
::: {data-id="box1" auto-animate-delay="0" style="background: #2780e3; width: 200px; height: 150px; margin: 10px;"}
:::

::: {data-id="box2" auto-animate-delay="0.1" style="background: #3fb618; width: 200px; height: 150px; margin: 10px;"}
:::

::: {data-id="box3" auto-animate-delay="0.2" style="background: #e83e8c; width: 200px; height: 150px; margin: 10px;"}
:::
:::


## Auto-Animate {auto-animate="true" auto-animate-easing="ease-in-out"}

Automatically animate matching elements across slides with Auto-Animate.

::: r-stack
::: {data-id="box1" style="background: #2780e3; width: 350px; height: 350px; border-radius: 200px;"}
:::

::: {data-id="box2" style="background: #3fb618; width: 250px; height: 250px; border-radius: 200px;"}
:::

::: {data-id="box3" style="background: #e83e8c; width: 150px; height: 150px; border-radius: 200px;"}
:::
:::

## Tabsets {.smaller .scrollable transition="slide"}

::: panel-tabset
### Plot

```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess")
```

### Data

```{r}
knitr::kable(mtcars)
```
:::

## Interactive Slides {.smaller transition="slide"}

Include Jupyter widgets and htmlwidgets in your presentations

```{r}
#| echo: false
#| fig-height: 5
library(leaflet)
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
```


## Preview Links

Navigate to hyperlinks without disrupting the flow of your presentation.

Use the `preview-links` option to open links in an iframe on top of your slides. Try clicking the link below for a demonstration:

::: {style="text-align: center; margin-top: 1em"}
[Matplotlib: Visualization with Python](https://matplotlib.org/){preview-link="true" style="text-align: center"}
:::
